---
surname: Alyssa Daigle
position: "Master's Student, Microbiology"
address: "Department of Molecular, Cellular, and Biomedical Sciences; University of New Hampshire"
email: "alyssa.daigle@unh.edu"
github: alyssa-daigle
linkedin: Alyssa Daigle
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(gsheet)
sheet_url <- "https://docs.google.com/spreadsheets/d/1pBwj_E2oTeOA0wRmqS0nxHKdIJkeSI-4U3SxY4tMPng/edit?usp=sharing"
```

<!-- # Research Interests  -->

<!-- Plant-microbe interactions; limnology; green manures -->

# Education 

``` {r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Location,~ Details,
  
  "Master of Science, Microbiology", 
  "Expected 2025", 
  "University of New Hampshire", 
  "Durham, New Hampshire",
    list("GPA: 4.00"),
  
"Bachelor of Science, Environmental Conservation and Sustainability",
"2019 - 2023",
"University of New Hampshire",
"Durham, New Hampshire",
  "Summa cum Laude"
) %>%
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution, 
                   where = Location, 
                   why = Details
  )
```


# Research Experience

```{r}
tribble(
  ~ Position,
  ~ Year,
  ~ Institution,
  ~ Location,
  ~ Details,
  
  "O'Brien Lab",
  "2023 - Present",
  "Master's Student - Advisor: Dr. Anna O'Brien",
  "University of New Hampshire",
  list("Developing high-throughput microcosm experiments to assess role of duckweed genotypes, co-occurring species, and microbiomes in green manure quality", "Investigating human health risk associated with occurrence of toxic cyanobacteria in green manures and fertilized crops", "Preparing and maintaining cultures of aquatic plants, microbes, and toxic cyanobacteria"),
  
  "Lakes Lay Monitoring Program",
  "2022 - 2023",
   "Laboratory/Field Technician",
  "University of New Hampshire",
    list("Sampled New Hampshire lakes and ponds at varying thermal depths to assess overall system health",
         "Performed nutrient analyses (phosphorus and nitrogen) on water samples using oxidative digestions and spectrophotometry",
         "Analyzed chemical and physical properties of water samples using titrations, spectrophotometry, and benchtop probes",
         "Managed large databases of historical limnological data to write annual highlight reports"),
  
"Ecotoxicology Lab",
"2021",
"Independent Study - Advisors: Dr. James Haney and Dr. Amanda McQuaid",
"University of New Hampshire",
  list("Analyzed aerosolized cyanobacterial picgments (chlorophyll, phycocyanin, and phycoerythrin) under varying temperature differentials using fluorometry to assess the human healh risks of aerosolized cyanotoxins in lakes",
       "Presented relevant findings/questions to Ecotoxicology Research Lab and poster presentation at UNH Undergraduate Research Conference")
       
) %>%
  detailed_entries(
    with = Position,
    when = Year,
    what = Institution,
    where = Location,
    why = Details
  )
```

# Presentations
 **Daigle, A.**, Dennehy, K., Haney, J., & McQuaid, A. (2022, April). Potential Drivers of Aerosolized Lake Toxins Impacting Public Health. Poster presented at Undergraduate Research Conference, University of New Hampshire.  

# Teaching Experience
``` {r}
tribble(
  ~ Position,
  ~ Year,
  ~ Institution,
  ~ Location,
  ~ Details,
  "Graduate Teaching Assistant - BMS 407: Germs 101",
  "08/2023 - 12/2023",
  "University of New Hampshire",
  "Durham, New Hampshire",
  "Moderated Zoom lectures, graded students, monitored class email account, managed course Canvas page"
) %>%
  detailed_entries(
    with = Position,
    when = Year,
    what = Institution,
    where = Location,
    why = Details
  )
```

# Awards
```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Location,
  
  "University of New Hampshire", 
  "2019 - 2023", 
  "Dean's Scholarship", 
  "$2,500/year"
  
) %>%
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution, 
                   where = Location,
  )

#(pH, SPCD, chloride, alkalinity, turbidity, dissolved color, Chlorophyll-a, dissolved oxygen, carbon dioxide)"
```

# Relevant Skills

**Computational**: R, ArcGIS Pro, Microsoft Suite

**Laboratory**: Microbial isolation and culturing; aquatic plant culturing; microscopy; chemical nutrient analyses; spectrophotometry; fluorometry; turbidometry; benchtop probe analysis; making reagents, media, and other solutions

**Field**: YSI multi-probe and flow systems measurement, thermal and point lake sampling

**Other**: Trained in Chemical Environmental Management System (CEMS), Adhered to EPA approved Quality Assurance Project Plans (QAPPs) at LLMP 

