---
name: Alyssa Daigle
position: "Master's Student"
address: "Department of Molecular, Cellular, and Biomedical Sciences; University of New Hampshire"
phone: 603 973 5565
www: insert web link
email: "alyssa.daigle@unh.edu"
github: alyssa-daigle
linkedin: Alyssa Daigle
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(gsheet)
sheet_url <- "https://docs.google.com/spreadsheets/d/1pBwj_E2oTeOA0wRmqS0nxHKdIJkeSI-4U3SxY4tMPng/edit?usp=sharing"
```

# Research Interests 

Plant-microbe interactions: duckweed as a green manure, effect of co-occurring species on green manure quality; specific interest in effect of cyanotoxins on safety of green manure

# Education 

``` {r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Location,~ Details,
  
  "Master of Science, Microbiology", 
  "Expected 2025", 
  "University of New Hampshire", 
  "Durham, New Hampshire",
    list("Advisor: Dr. Anna O'Brien", 
         "Research: green manure quality"),
  
"Bachelor of Science, Environmental Conservation and Sustainability",
"May 2023",
"University of New Hampshire",
"Durham, New Hampshire",
  "Summa Cum Laude"
) %>%
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution, 
                   where = Location, 
                   why = Details
  )
```

# Prior Experience

```{r}
tribble(
  ~ Position,
  ~ Year,
  ~ Institution,
  ~ Location,
  ~ Details,
  "Laboratory/Field Technician",
  "2022-2023",
  "Lakes Lay Monitoring Program, University of New Hampshire",
  "Durham, New Hampshire",
    "Water quality monitoring of NH lakes, ponds, and tributaries",
  
"Undergraduate Researcher",
"2021",
"Ecotoxicology Lab, University of New Hampshire",
"Durham, New Hampshire",
  "Researching the effect of aerosolized cyanotoxins"
) %>%
  detailed_entries(
    with = Position,
    when = Year,
    what = Institution,
    where = Location,
    why = Details
  )
```

# Presentations
**Daigle, A.**, Dennehy, K., Haney, J., & McQuaid, A. (2022, April). Potential Drivers of Aerosolized Lake Toxins Impacting Public Health. Poster presented at Undergraduate Research Conference, University of New Hampshire.  
 

# Teaching Experience
``` {r}
tribble(
  ~ Position,
  ~ Year,
  ~ Institution,
  ~ Location,
  ~ Details,
  "Germs 101 Teaching Assistant",
  "Fall 2023",
  "University of New Hampshire",
  "Durham, New Hampshire",
  "teaching assistant for class"
) %>%
  detailed_entries(
    with = Position,
    when = Year,
    what = Institution,
    where = Location,
    why = Details
  )
```

# Relevant Skills


# Education 

<!-- # ``` {r education} -->
<!-- # Education <- gsheet::gsheet2tbl(sheet_url, sheet="Education") %>% -->
<!-- #   vitae::detailed_entries(what = Degree, -->
<!-- #                           when = Year, -->
<!-- #                           with = Institution,  -->
<!-- #                           where = Location,  -->
<!-- #                           why = Details) -->
<!-- #  -->