---
surname: Alyssa Daigle
position: "Master's Student, Microbiology"
address: "Department of Molecular, Cellular, and Biomedical Sciences; University of New Hampshire"
www: insert web link
email: "alyssa.daigle@unh.edu"
github: alyssa-daigle
linkedin: Alyssa Daigle
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(gsheet)
sheet_url <- "https://docs.google.com/spreadsheets/d/1pBwj_E2oTeOA0wRmqS0nxHKdIJkeSI-4U3SxY4tMPng/edit?usp=sharing"
```

# Research Interests 

Plant-microbe interactions; duckweed green manures; effect of genotypes and co-occurring species on green manure quality; effect of cyanotoxins on safety of green manure

# Education 

``` {r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Location,~ Details,
  
  "Master of Science, Microbiology", 
  "08/2023 - Present", 
  "University of New Hampshire", 
  "Durham, New Hampshire",
    list("Advisor: Dr. Anna O'Brien"),
  
"Bachelor of Science, Environmental Conservation and Sustainability",
"08/2019 - 05/2023",
"University of New Hampshire",
"Durham, New Hampshire",
  "Summa Cum Laude"
) %>%
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution, 
                   where = Location, 
                   why = Details
  )
```

# Prior Experience

```{r}
tribble(
  ~ Position,
  ~ Year,
  ~ Institution,
  ~ Location,
  ~ Details,
  "Laboratory/Field Technician",
  "03/2022 - 08/2023",
  "Lakes Lay Monitoring Program, University of New Hampshire",
  "Durham, New Hampshire",
    list("Sampled New Hampshire lakes and ponds at varying thermal depths to assess overall system health",
         "Performed nutrient analyses (total phosphorus, soluble reactive phosphorus, total nitrogen) on water samples using oxidative digestions and spectrophotometry",
         "Analyzed chemical and physical properties of water samples (pH, SPCD, chloride, alkalinity, turbidity, dissolved color, Chlorophyll-a, dissolved oxygen, carbon dioxide)",
         "Wrote annual highlight reports"),
  
"Undergraduate Researcher",
"01/2021 - 05/2021",
"Ecotoxicology Lab, University of New Hampshire",
"Durham, New Hampshire",
  list("Analyzed aerosolized chlorophyll, phycocyanin, and phycoerythrin pigments (cyanobacteria proxy) under varying temperature differentials using fluorometry to assess the risk of aerosolized cyanotoxins",
       "Presented relevant findings/questions to Ecotoxicology Research Lab and poster presentation at Undergraduate Research Conference (UNH)")
       
) %>%
  detailed_entries(
    with = Position,
    when = Year,
    what = Institution,
    where = Location,
    why = Details
  )
```

# Presentations
**Daigle, A.**, Dennehy, K., Haney, J., & McQuaid, A. (2022, April). Potential Drivers of Aerosolized Lake Toxins Impacting Public Health. Poster presented at Undergraduate Research Conference, University of New Hampshire.  
 

# Teaching Experience
``` {r}
tribble(
  ~ Position,
  ~ Year,
  ~ Institution,
  ~ Location,
  ~ Details,
  "BMS 407: Germs 101 - Graduate Teaching Assistant",
  "08/2023 - 12/2023",
  "University of New Hampshire",
  "Durham, New Hampshire",
  "Moderated Zoom lectures, graded students, monitored class email account"
) %>%
  detailed_entries(
    with = Position,
    when = Year,
    what = Institution,
    where = Location,
    why = Details
  )
```

# Relevant Skills

*Computational*: R/RStudio, Microsoft Suite

*Wet Lab*: Spectrophotometry, Fluorometry, Turbidometry, Benchtop probe analysis, YSI multi-probe and flow systems measurement, Plankton towing, Tube and point lake sampling, Secchi disk measurement 

*Other*: Trained in Chemical Environmental Management System (CEMS), Adhere to EPA approved Quality Assurance Project Plans (QAPPs) at LLMP 
